%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{amssymb}
\usepackage{fontspec}
\setmainfont{texgyrepagella}[
  Extension = .otf,
  UprightFont = *-regular,
  BoldFont = *-bold,
  ItalicFont = *-italic,
  BoldItalicFont = *-bolditalic
]
% glyphtounicode not needed for XeTeX/tectonic


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.9in}
\addtolength{\textheight}{1.9in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\bfseries\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% ATS parsable by default with XeTeX

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\newcommand{\resumeAuthors}[1]{
    \vspace{-7pt}\par\noindent\hspace{0.01in}\begin{minipage}[t]{0.96\textwidth}\small #1\end{minipage}\vspace{-3pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}, topsep=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-4pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge Yaofeng Su} \\ \vspace{1pt}
    \small \href{mailto:yfsu23@m.fudan.edu.cn}{\underline{yfsu23@m.fudan.edu.cn}} $|$
    \href{https://github.com/InfiniteLoopCoder}{\underline{GitHub: InfiniteLoopCoder}}, 3.3k stars $|$
    \href{https://scholar.google.com/citations?user=ASn1XLAAAAAJ}{\underline{Google Scholar}}, 150 citations
\end{center}
\vspace{-8pt}
\section{Research Interest}
\begin{itemize}[leftmargin=0.15in, label={}]
\item\small My research interest lies in multimodal generative models as a means to build faithful world representations. Through RL, distillation, and agent frameworks, I have contributed to audio-visual generation, autonomous driving, and video understanding. Going forward, I aim to advance multimodal foundation models with principled theoretical insights.
\end{itemize}\vspace{-14pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Fudan University}{Shanghai, China}
      {B.S. in Computer Science}{Sep. 2023 -- Jul. 2027}
      \resumeItemListStart
        \resumeItem{GPA 3.84/4.00, Rank 7/97. Advised by \textbf{Prof.\ Wenchao Ding} on autonomous driving risk assessment.}
      \resumeItemListEnd
    \resumeSubheading
      {University of North Carolina at Chapel Hill}{Chapel Hill, NC}
      {Exchange Student}{Aug. 2025 -- Dec. 2025}
      \resumeItemListStart
        \resumeItem{Dean's List. Researched VLA models and LLM agents under the supervision of \textbf{Prof.\ Huaxiu Yao}.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------REPRESENTATIVE HONORS AND AWARDS-----------
\section{Representative Honors}
  \resumeSubHeadingListStart
    \resumeProjectHeading{\textbf{Tencent Outstanding Student Award} (Hunyuan Team)}{Sep. 2025}
    \resumeProjectHeading{\textbf{Fudan University Outstanding Student Award} (Top 8\%)}{Oct. 2024}
  \resumeSubHeadingListEnd


%-----------INTERNSHIP EXPERIENCE-----------
\section{Internship Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Joy Future Academy, JD}{Dec. 2025 -- Present}
      {Intern, Multimodal Foundation Model Research Department}{}
      \resumeItemListStart
        \resumeItem{Developed audio-visual distillation algorithms and real-time streaming generation architectures. Core contributor to OmniForcing (ECCV 2026) and JoyAI-Echo. Currently exploring world models with memory mechanisms. Supervised by \textbf{Zeyue Xue}.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------INVITED TALKS-----------
\section{Invited Talks}
  \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{Invited Talk, Lightricks (LTX-Video Team)}}{May 2026}
        \resumeItemListStart
          \resumeItem{Presented joint audio-visual streaming generation and self-forcing distillation methodology to Lightricks' CTO and Director of GenAI Research, covering LTX-2 foundation model adaptation and ongoing LTX-2.3 collaboration.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PUBLICATIONS-----------
\section{Publications}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{OmniForcing: Unleashing Real-time Joint Audio-Visual Generation}}{ECCV 2026, \textbf{Oral}}
          \resumeAuthors{\underline{Yaofeng Su}*, Yuming Li*, Zeyue Xue, Jie Huang, Siming Fu, Haoran Li, Haoyang Huang, Nan Duan}
          \resumeItemListStart
            \resumeItem{Designed asymmetric block-causal alignment and joint self-forcing distillation to convert offline bidirectional audio-visual diffusion models into real-time streaming generators at 25 FPS. Featured as a representative real-time audio-visual generation baseline in Alibaba Wan Streamer.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{SimpleMem: Efficient Lifelong Memory for LLM Agents}}{ICML 2026}
          \resumeAuthors{Jiaqi Liu*, \underline{Yaofeng Su}*, Peng Xia, Siwei Han, Zeyu Zheng, Cihang Xie, Mingyu Ding, Huaxiu Yao}
          \resumeItemListStart
            \resumeItem{Designed semantic structured compression and intent-aware retrieval for LLM agent lifelong memory, improving F1 by 26.4\% on LoCoMo while reducing token consumption by 30$\times$.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Learning a Unified Risk Map for Autonomous Driving in Partially Observable Environments}}{IEEE RA-L 2026}
          \resumeAuthors{Jie Jia*, \underline{Yaofeng Su}*, Zeyu Bao, Yun Hong, Bingzhao Gao, Zhongxue Gan, Wenchao Ding}
          \resumeItemListStart
            \resumeItem{Addressed occlusion-induced collision risk in autonomous driving by modeling hidden vehicle motion distributions with adversarial-guided diffusion, enabling risk-aware planning without full observability.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{ReAgent-V: A Reward-Driven Multi-Agent Framework for Video Understanding}}{NeurIPS 2025}
          \resumeAuthors{Yiyang Zhou*, Yangfan He*, \underline{Yaofeng Su}, Siwei Han, Joel Jang, Gedas Bertasius, Mohit Bansal, Huaxiu Yao}
          \resumeItemListStart
            \resumeItem{A multi-agent framework that leverages video understanding to generate reward signals for downstream tasks. Contributed reward-based VLA post-training, surpassing RL baselines by 9.8\% on VLA alignment.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{JoyAI-Echo: Pushing the Frontier of Long Audio-Visual Generation}}{Tech Report, 2026}
          \resumeAuthors{Echo Team @ Joy Future Academy, JD}
          \resumeItemListStart
            \resumeItem{A long-form multi-shot framework with cross-modal memory and DMD distillation, achieving 7.5$\times$ inference speedup and minute-level coherent audio-video story generation.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming}{: Python, C/C++, PyTorch, Triton, Linux, Git, Docker} $|$ \textbf{Languages}{: English (TOEFL 108)} \\
     \textbf{AI}{: Reinforcement Learning, Diffusion Models and SDE, LLM/VLM Distillation, Distributed Training, AI Agent, Algorithm Analysis}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
